\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

\title{Robust Window-Period and Marker Detection\\\large RMCPE + TCIML Specification}
\author{Echpressure}
\date{\today}

\begin{document}
\maketitle

\section{Purpose}
This document specifies a two-stage preprocessing pipeline for periodic waveforms:
\begin{enumerate}
  \item \textbf{RMCPE} (Robust Multi-file Comb Period Estimation) estimates a stable global period $\hat{T}$ across files.
  \item \textbf{TCIML} (Template-Constrained Incident Marker Localization) finds per-file marker indices using $\hat{T}$ and a learned template.
\end{enumerate}
The goal is robust marker localization under noise, amplitude variation, and occasional outlier files.

\section{Stage 1: RMCPE (Global Period Estimation)}
Given files $i \in \{1,\dots,M\}$ with samples $x_i[n]$, search $T \in [T_{\min}, T_{\max}]$ on a grid.

For each file and candidate period, score periodic agreement with a robust objective:
\begin{equation}
S_i(T) = \sum_{n} \rho\!\left(x_i[n]-x_i[n+T]\right),
\end{equation}
where $\rho(\cdot)$ is a robust loss (Huber-like in implementation) to reduce outlier influence.

For each file, fit a local optimum $\hat{T}_i$ and confidence weight $w_i$ from residual scale and fit quality.
Aggregate to a global estimate:
\begin{equation}
\hat{T} = \frac{\sum_i w_i\hat{T}_i}{\sum_i w_i}.
\end{equation}

Exported artifacts:
\begin{itemize}
  \item \texttt{window\_period\_summary.json} containing $\hat{T}$ and aggregate diagnostics.
  \item \texttt{window\_period\_per\_file.csv} containing $\hat{T}_i$, scores, and weights.
\end{itemize}

\section{Stage 2: TCIML (Marker Localization)}
Using $\hat{T}$, each file is normalized and aligned to expected cycle centers:
\begin{equation}
\mu_k = \phi + k\hat{T}, \quad k=0,1,\dots,K-1,
\end{equation}
where $\phi$ is an estimated phase offset.

A template waveform is built from selected cycles (trimmed mean/median style robustness). Marker candidates are scored by local template match with timing regularization:
\begin{equation}
J(n_k) = \alpha\,\mathrm{match}(x[n_k],\tau) - \beta\,\left|n_k-\mu_k\right|,
\end{equation}
subject to spacing constraints near $\hat{T}$.

The final marker set is the sequence maximizing total score under constraints (dynamic-programming style selection).

Outputs:
\begin{itemize}
  \item marker index table per file,
  \item optional diagnostic overlays (template and selected markers).
\end{itemize}

\section{Operational Notes}
\begin{itemize}
  \item Use manual period override when known from acquisition hardware.
  \item Keep robust weighting enabled for mixed-quality batches.
  \item Validate marker spacing histogram around $\hat{T}$ as a sanity check.
\end{itemize}

\section{Implementation Map}
Reference implementation modules:
\begin{itemize}
  \item \texttt{src/echopress/core/rmcpe.py}
  \item \texttt{src/echopress/core/tciml.py}
  \item CLI integration: \texttt{src/echopress/cli.py}
\end{itemize}

\section{Regeneration}
Build this PDF locally with:
\begin{verbatim}
make docs-algorithms
\end{verbatim}

\end{document}
